Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-14 latex/article.tex
abstract

\author{xxx}

 \institute{ CNRS,  LIRIS, UMR5205, F-69621, France\\
   %\email{david.coeurjolly@liris.cnrs.fr}
}
\graphicspath{{./Figs/}}
\input{macros}
\begin{document}
\maketitle

\begin{abstract}\sloppy

>>>>

\author{H\'el\`ene Perrier\inst{1}\and J\'eré\'emy Levallois\inst{1}\and  David Coeurjolly\inst{1}\and  Jonathan
  Dupuy\inst{1}\inst{2}\and   Jean-Philippe Farrugia\inst{1}\and Jean-Claude Iehl\inst{1}\and Jacques-Olivier Lachaud\inst{3} }

%\address[liris]{Universit\'e de Lyon, CNRS, INSA-Lyon, LIRIS, UMR5205, F-69621, France}
%\address[lama]{Universit\'e de Savoie, CNRS, LAMA, UMR 5127, F-73776, France}

 \institute{ Universit\'e de Lyon, CNRS\\
   INSA-Lyon, LIRIS, UMR5205, F-69621, France
%   \email{\{david.coeurjolly,jeremy.levallois\}@liris.cnrs.fr}
   \and
 Universit\'ee de Montr\'eeal\\
LIGUM, Dept. I.R.O., Canada\\
\and
Universit\'e de Savoie, CNRS\\
LAMA, UMR5127, F-73776, France\\
%\email{jacques-olivier.lachaud@univ-savoie.fr}
}

\graphicspath{{./Figs/}}
\input{macros}
\begin{document}
\maketitle

\begin{abstract}\sloppy
  Interactive visualization is a very convenient tool to explore
  complex scientific data or to explore different parameter settings
  for a given processing algorithm. In article, we present a tool to
  efficiently explore the curvature tensor on the boundary of
  potentially large digital object. More precisely, we combine a fully
  parallel pipeline on GPU to extract an adaptive triangulated
  iso-surface of the digital object, with a curvature tensor
  estimation at each surface point based on integral invariants. Integral
  invariants being parametrized by a given ball radius, our proposal
  allows us to explore interactively different radii and thus select
  the appropriate scale to perform the computations (mean and gaussian
  curvature, principal curvatures, principal directions and normal
  vector field).
